%-------------------------
% Resume in Latex
% Author : Jessica Hamilton
% Website: https://github.com/jessicant/hamiltonResume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/jessicant}{\Large Jessica Hamilton}} & Email : \href{mailto:jesshamilton159@gmail.com}{jesshamilton159@gmail.com}\\
  \href{https://github.com/jessicant}{github.com/jessicant} & Mobile : +1-360-913-2491 \\
\end{tabular*}


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
    {Amazon Web Services (AWS) DynamoDB}{Seattle, WA}
    {Software Engineer}{January 2023 -- Present}
    \resumeItemListStart
      \resumeItem{Live Replication Ledger Sweeper}
        {Negotiated the end-to-end design with engineering leadership and launched a safety-first cleanup system for the live replication ledger, striking the balance between cross-region sync, investigation trails, and GDPR/CCPA/HIPAA retention limits.}
      \resumeItem{Metadata Cleanup Sweeper}
        {Blueprinted and implemented a scalable sweeper for a critical metadata table, safely reducing 1.1M entries to 100K; cut replication delays from six hours to five minutes and restored customer-facing consistency checks.}
      \resumeItem{Global Tables GDPR Compliance}
        {Launched a six-engineer workstream, auditing partner teams and later advising as a consultant so global tables teams could replace the 36 dev-days per quarter of risky manual cleanups with safe automation that keeps privacy promises.}
      \resumeItem{Intern Mentorship \& GDPR Automation}
        {Coached a first-time intern on my team from classroom experience to a return offer, teaching safe data-handling patterns and code quality so we could automate privacy deletions across regions without regressions.}
      \resumeItem{Multi-Region Consistency Cleanup}
        {Owned design-to-launch of a release-blocking strong-consistency feature that tightened the replica delete workflow, eliminating the orphaned encrypted copies table deletes used to leave behind in some regions and keeping the launch privacy-safe.}
      \resumeItem{Monitoring \& Dashboards}
        {Defined 22 product-focused KPIs and built dashboards translating raw metrics into leadership-friendly signals; dashboards were used in senior leadership go/no-go launch decisions.}
    \resumeItemListEnd

  \resumeSubheading
    {Amazon Web Services (AWS) DynamoDB}{Seattle, WA}
    {Software Engineering Intern}{June 2022 -- September 2022}
    \resumeItemListStart
      \resumeItem{Workflow Parallelization}
        {Optimized internal testing tool used by 300+ DynamoDB engineers; designed and implemented multithreaded setup that cut environment provisioning time from 5h to 30m at p99, accelerating service development and launch velocity.}
    \resumeItemListEnd
 \resumeSubHeadingListEnd

%-----------VOLUNTEER WORK-----------------
\section{Volunteer}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Camp Oasis}{Seattle, WA}
      {Volunteer Instructor}{Summer 2025}
      \resumeItemListStart
        \resumeItem{Teaching}
          {Led and taught a class of 50+ students (ages 6--13) living with Crohn’s disease or ulcerative colitis, introducing programming fundamentals through Scratch.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubheading
      {GDPR-Friendly Key-Value Store}{\href{https://github.com/jessicant/GDPR-KV}{GitHub} \textbar{} \href{https://docs.google.com/document/d/1oFiOTBT4e-9KTA5CQ2Vl7vVi_JmQf0DTA2GCq-XslmY/edit?tab=t.0}{Design Doc}}
      {Designer \& Developer}{2025}
      \resumeItemListStart
        \resumeItem{Subject-Centric Data Layer}
          {Added subject→keys mapping and API (Create, Put, Get, Delete) with validations, tombstoning, and precise retention.}
        \resumeItem{Tamper-Evident Audit Trail}
          {Built append-only audit log with hash chaining, request IDs, and granular event types for immutable replay.}
        \resumeItem{Erasure \& Retention Engine}
          {Designed PurgeSweeper with GSI + transactional deletes to ensure provable, idempotent erasure post-retention.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd



%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Washington}{Seattle, WA}
      {BA with Concentration in Information Systems; GPA: 3.89}{Sep. 2018 -- Dec. 2021}
  \resumeSubHeadingListEnd
  %-------------------------------------------
  %-------- SKILLS------------
  \section{Skills}
\resumeItemListStart
  \resumeItem{Languages}{Java (primary), Python, SQL, Rust, Bash}
  \resumeItem{Services}{DynamoDB, IAM, KMS, EC2, CDK, CloudWatch}
  \resumeItem{Privacy \& Compliance Law}{GDPR/CCPA/HIPAA regulations, data lifecycle governance, automated cleanup workflows}
\resumeItemListEnd

\end{document}
